---
title: "Open Payments Figures"
author: "Quinn White"
date: "`r Sys.Date()`"
output: 
   pdf_document:
     toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, out.width="100%", fig.height=4, echo=FALSE,cache=TRUE, message=FALSE, warning=FALSE)
library(tidyverse)
library(here)


theme_c <- function(...){ 
   # font <- "Helvetica"   #assign font family up front
    theme_bw() %+replace%    #replace elements we want to change
    
    theme(
      
      
      #text elements
      plot.title = element_text(             #title
                   size = 13,                #set font size
                   face = 'bold',            #bold typeface
                   hjust = .5,
                   vjust = 3,
                   margin=margin(0,0,2,0)),               
      
      plot.subtitle = element_text(          #subtitle
                   size = 11,
                   hjust = .5,
                   face = 'italic',
                   vjust = 3),               #font size
      
      axis.title = element_text(             #axis titles
                   size = 12),               #font size
      
      axis.text = element_text(              #axis text
                   size = 9),
      legend.text = element_text(size = 12),
      legend.title = element_text(size=14),
      # t, r, b, l
      plot.margin = unit(c(1,.5,.5,.5), "cm"),
      legend.position = "right",
      strip.text.x = element_text(size = 12,color="white"),
      strip.background = element_rect(fill = "#3E3D3D")
      ) %+replace%
      theme(...)
   
}


```


# Making Many Identical Payments on the Same Date

Looked at several examples where:

- All payments for a company on a specific date where the same
- There were more than 20 identical payments
- Total amount of payments was greater than $100


This is not an exhaustive search through the entire dataset (11,408,131 rows).


```{r load-data}

# general payments data file
general <- data.table::fread(here('data/OP_DTL_GNRL_PGYR2021_P01202023.csv'),
                             nrows=1e6) %>%
  mutate(date = as_date(Date_of_Payment, format = "%m/%d/%Y"))  



max_example <- general %>%
  mutate(date = as_date(Date_of_Payment, format = "%m/%d/%Y"))  %>%
  filter(Nature_of_Payment_or_Transfer_of_Value == "Food and Beverage") %>%
  group_by(Applicable_Manufacturer_or_Applicable_GPO_Making_Payment_Name, date) %>%
  mutate(n_payments =n(),
            unique = n_distinct(Total_Amount_of_Payment_USDollars)) %>%
  ungroup() %>%
  filter(unique ==1 & n_payments >20 & Total_Amount_of_Payment_USDollars >100)  %>%
  select(date, 
         Applicable_Manufacturer_or_Applicable_GPO_Making_Payment_Name, 
         Total_Amount_of_Payment_USDollars,
         Covered_Recipient_NPI,
         n_payments)


max_example <- max_example %>%
  group_by(Applicable_Manufacturer_or_Applicable_GPO_Making_Payment_Name) %>%
  # only keep one date per company
  # SYnthes GmbH is the only one with repeats
  slice_max(n=1, order_by=date) %>%
  ungroup()


rm(general)


```

## Plot Including All Examples

```{r, fig.width=10, fig.height=7}

# faceted bar chart for example companies 

max_example %>%
  rename(company = Applicable_Manufacturer_or_Applicable_GPO_Making_Payment_Name) %>%
  mutate(Covered_Recipient_NPI = as.character(Covered_Recipient_NPI),
         company = paste0(company,"\n", format(date, "%b %d %Y"))) %>%
  mutate(company = gsub(" 2021", ", 2021", company)) %>%
  ggplot(aes(x=Covered_Recipient_NPI, y = Total_Amount_of_Payment_USDollars)) +
  geom_bar(stat="identity") +
  facet_wrap(~fct_reorder(company,
                          Total_Amount_of_Payment_USDollars,
                          .desc=TRUE),
             scales="free_x") +
  theme_c(axis.text.x= element_text(angle=60, size=4)) +
  scale_y_continuous(labels=scales::dollar) +
  labs(y = "Total Amount Paid in Dollars",
       x = "Covered Recipient Identifier (NPI)",
       title= "Examples Where Companies Paid an Identical\nAmount to Many Providers on a Single Date")

```


## Table of All Examples

```{r}

library(kableExtra)

max_example %>%
  mutate(Total_Amount_of_Payment_USDollars=paste0("$",Total_Amount_of_Payment_USDollars)) %>%
  select(Company = Applicable_Manufacturer_or_Applicable_GPO_Making_Payment_Name,
         Date=date,
        `Number of Payments` = n_payments,
        `Payment` = Total_Amount_of_Payment_USDollars) %>%
  distinct()%>%
  arrange(desc(`Number of Payments`)) %>%
  kbl(caption = "Examples of Companies that Made Identical Payments to Many Providers on a Single Date",
      booktabs=TRUE) %>%
  kable_styling(latex_options="hold_position")



```


## Individual Plots for Each Example

```{r}

companies <- unique(max_example$Applicable_Manufacturer_or_Applicable_GPO_Making_Payment_Name)

walk(companies, ~{
  
  company_data <- max_example %>%
    rename(company = Applicable_Manufacturer_or_Applicable_GPO_Making_Payment_Name) %>%
    filter(company == .x) %>%
    mutate(Covered_Recipient_NPI = as.character(Covered_Recipient_NPI),
           company = paste0(company," on ", format(date, "%b %d %Y"))) %>%
    mutate(company = gsub(" 2021", ", 2021", company)) 
    
  plt <- company_data %>%
    ggplot(aes(x=Covered_Recipient_NPI, y = Total_Amount_of_Payment_USDollars)) +
    geom_bar(stat="identity") +
    theme_c(axis.text.x= element_text(angle=60, size=5)) +
    scale_y_continuous(labels=scales::dollar) +
    labs(y = "Total Amount Paid in Dollars",
         x = "Covered Recipient Identifier (NPI)",
         title = unique(company_data$company),
         subtitle = "Example Where a Company Paid an Identical\nAmount to Many Providers on a Single Date")
  
  print(plt)
    
})

```




# Considering Provider Types by Year


Considering payments by covered recipient type.

```{r get-2021, fig.width=9,fig.height=4}

# 11408131 rows total
general_names <- data.table::fread(
  here('data/OP_DTL_GNRL_PGYR2021_P01202023.csv'),
  skip=0,nrows=2)  %>%
  colnames()



###############################################################
# ITERATE BY CHUNK TO HANDLE LARGE FILE SIZES (2021)
###############################################################

# get number of rows in full dataset in the terminal with:
# wc -l OP_DTL_GNRL_PGYR2021_P01202023.csv
chunk_size <- ceiling(1140813/20)

chunks <- tibble(end = (1:20)*chunk_size) %>%
  mutate(begin =  lag(end,n=1)) %>%
  # first observation will have NA observation when we lag
  # so set this one to 1
  mutate(begin = ifelse(is.na(begin),1, begin),
         begin =ifelse(begin!=1, begin+1, begin))



type_summary <- pmap_df(chunks, function(begin,end) {
  
  message(paste("skip =", begin, "end_index = ",begin+chunk_size))
    n_rows <- ifelse(begin+chunk_size > 1140813,1140813-begin, chunk_size )

    dat <- data.table::fread(here('data/OP_DTL_GNRL_PGYR2021_P01202023.csv'),
          skip = begin,
          nrows = n_rows,
          col.names = general_names,
          colClasses="character") 
    # number of payments in each category
    by_type <- dat %>%
      group_by(Covered_Recipient_Type) %>%
      summarize(n = n())
  })


type_summary_2021 <- type_summary %>%
  group_by(Covered_Recipient_Type) %>%
  summarize(n = sum(n)) 




###############################################################
# ITERATE BY CHUNK TO HANDLE LARGE FILE SIZES (2019)
###############################################################

# get number of rows in full dataset in the terminal with:
# wc -l OP_DTL_GNRL_PGYR2021_P01202023.csv
chunk_size <- ceiling(1140813/20)

chunks <- tibble(end = (1:20)*chunk_size) %>%
  mutate(begin =  lag(end,n=1)) %>%
  # first observation will have NA observation when we lag
  # so set this one to 1
  mutate(begin = ifelse(is.na(begin),1, begin),
         begin =ifelse(begin!=1, begin+1, begin))



type_summary_2021 <- pmap_df(chunks, function(begin,end) {
  
   n_rows <- ifelse(begin+chunk_size > 1140813,1140813-begin, chunk_size )

  message(paste("skip =", begin, "end_index = ",begin+chunk_size))
  
    dat <- data.table::fread(here('data/OP_DTL_GNRL_PGYR2021_P01202023.csv'),
          skip = begin,
          nrows = n_rows,
          col.names = general_names,
          colClasses="character") 
    # number of payments in each category
    by_type <- dat %>%
      group_by(Covered_Recipient_Type) %>%
      summarize(n = n())
  })




type_summary_2021 <- type_summary_2021 %>%
  group_by(Covered_Recipient_Type) %>%
  summarize(n = sum(n)) %>%
  mutate(year = 2021)




```


```{r}


###############################################################
# ITERATE BY CHUNK TO HANDLE LARGE FILE SIZES (2021)
###############################################################

# get number of rows in full dataset in the terminal with:
# wc -l OP_DTL_GNRL_PGYR2021_P01202023.csv
chunk_size <- ceiling(1140813/20)

chunks <- tibble(end = (1:20)*chunk_size) %>%
  mutate(begin =  lag(end,n=1)) %>%
  # first observation will have NA observation when we lag
  # so set this one to 1
  mutate(begin = ifelse(is.na(begin),1, begin),
         begin =ifelse(begin!=1, begin+1, begin))



primary_type_summary_2021 <- pmap_df(chunks, function(begin,end) {
  
  n_rows <- ifelse(begin+chunk_size > 1140813,1140813-begin, chunk_size )
  
  message(paste("skip =", begin, "end_index = ",begin+chunk_size))
  
    dat <- data.table::fread(here('data/OP_DTL_GNRL_PGYR2021_P01202023.csv'),
          skip = begin,
          nrows = n_rows,
          col.names = general_names,
          colClasses="character") 
    # number of payments in each category
    by_type <- dat %>%
      group_by(Covered_Recipient_Type, Covered_Recipient_Primary_Type_1) %>%
      summarize(n = n())
  })


primary_type_summary_2021 <- primary_type_summary_2021 %>%
  group_by(Covered_Recipient_Type,Covered_Recipient_Primary_Type_1) %>%
  summarize(n = sum(n)) 


# type_summary <- pmap_df(chunks, function(begin,end) {
#     n_rows <- ifelse(begin+chunk_size > 1140813,1140813-begin, chunk_size )
# 
#   message(paste("skip =", begin, "end_index = ",begin+chunk_size))
#   
#     dat <- data.table::fread(here('data/OP_DTL_GNRL_PGYR2021_P01202023.csv'),
#           skip = begin,
#           nrows = n_rows,
#           col.names = general_names,
#           colClasses="character") 
#     # number of payments in each category
#     by_type <- dat %>%
#       group_by(Nature_of_Payment_or_Transfer_of_Value) %>%
#       summarize(n = n())
#   })
# 
# 
# type_summary_2021 <- type_summary %>%
#   group_by(Nature_of_Payment_or_Transfer_of_Value) %>%
#   summarize(n = sum(n)) 




###############################################################
# ITERATE BY CHUNK TO HANDLE LARGE FILE SIZES (2019)
###############################################################

# get number of rows in full dataset in the terminal with:
# wc -l OP_DTL_GNRL_PGYR2021_P01202023.csv
chunk_size <- ceiling(1140813/20)

chunks <- tibble(end = (1:20)*chunk_size) %>%
  mutate(begin =  lag(end,n=1)) %>%
  # first observation will have NA observation when we lag
  # so set this one to 1
  mutate(begin = ifelse(is.na(begin),1, begin),
         begin =ifelse(begin!=1, begin+1, begin))



type_summary_2021 <- pmap_df(chunks, function(begin,end) {
  
    n_rows <- ifelse(begin+chunk_size > 1140813,1140813-begin, chunk_size )

    
  message(paste("skip =", begin, "end_index = ",begin+chunk_size))
  
    dat <- data.table::fread(here('data/OP_DTL_GNRL_PGYR2021_P01202023.csv'),
          skip = begin,
          nrows = n_rows,
          col.names = general_names,
          colClasses="character") 
    # number of payments in each category
    by_type <- dat %>%
      group_by(Covered_Recipient_Type) %>%
      summarize(n = n())
  })




type_summary_2021 <- type_summary_2021 %>%
  group_by(Covered_Recipient_Type) %>%
  summarize(n = sum(n)) %>%
  mutate(year = 2021)

```




```{r get-2019}


# 11408131 rows total
general_names <- data.table::fread(here('data/OP_DTL_GNRL_PGYR2019_P01202023.csv'),
                             skip=0,nrows=2)  %>%
  colnames()



###############################################################
# ITERATE BY CHUNK TO HANDLE LARGE FILE SIZES (2019)
###############################################################

# get number of rows in full dataset in the terminal with:
# wc -l OP_DTL_GNRL_PGYR2019_P01202023.csv
chunk_size <- ceiling(1269126/10)

chunks <- tibble(end = (1:10)*chunk_size) %>%
  mutate(begin =  lag(end,n=1)) %>%
  # first observation will have NA observation when we lag
  # so set this one to 1
  mutate(begin = ifelse(is.na(begin),1, begin),
         begin =ifelse(begin!=1, begin+1, begin))



type_summary_2019 <- pmap_df(chunks, function(begin,end) {
  
    n_rows <- ifelse(begin+chunk_size > 1140813,1140813-begin, chunk_size )

  
  message(paste("skip =", begin, "end_index = ",begin+chunk_size))
  
    dat <- data.table::fread(here('data/OP_DTL_GNRL_PGYR2019_P01202023.csv'),
          skip = begin,
          nrows = n_rows,
          col.names = general_names,
          colClasses="character") 
    # number of payments in each category
    by_type <- dat %>%
      group_by(Covered_Recipient_Type) %>%
      summarize(n = n())
  })


type_summary_2019 <- type_summary_2019 %>%
  group_by(Covered_Recipient_Type) %>%
  summarize(n = sum(n))  %>%
  mutate(year=2019)






primary_type_summary_2019 <- pmap_df(chunks, function(begin,end) {
  
  n_rows <- ifelse(begin+chunk_size > 1140813,1140813-begin, chunk_size )
  
  message(paste("skip =", begin, "end_index = ",begin+chunk_size))
  
    dat <- data.table::fread(here('data/OP_DTL_GNRL_PGYR2019_P01202023.csv'),
          skip = begin,
          nrows = n_rows,
          col.names = general_names,
          colClasses="character") 
    # number of payments in each category
    by_type <- dat %>%
      group_by(Covered_Recipient_Type, Covered_Recipient_Primary_Type_1) %>%
      summarize(n = n())
  })


primary_type_summary_2019 <- primary_type_summary_2019 %>%
  group_by(Covered_Recipient_Type,Covered_Recipient_Primary_Type_1) %>%
  summarize(n = sum(n)) 





```


## By Covered Recipient Type 


```{r,fig.width=9,fig.height=4}

########################################
# faceted provider type by year plot
########################################


both <- type_summary_2021 %>%
  bind_rows(type_summary_2019)

both %>%
  mutate(Covered_Recipient_Type= gsub("Covered Recipient ", "",
                                      Covered_Recipient_Type),
         Covered_Recipient_Type = gsub(" ", "\n", Covered_Recipient_Type)) %>%
  ggplot(aes(x= fct_reorder(Covered_Recipient_Type,n, .desc=TRUE),
             y = n)) +
  geom_bar(stat="identity") +
  facet_grid(~year, space="free", scales="free_y") +
  theme_c(axis.title.x = element_text(margin=margin(15,0,0,0),
                                      size=15),
          axis.text.x=element_text(size=12),
          axis.title.y =element_text(size=15,angle=90),
           plot.title = element_text(face="bold", hjust = .5, size=14, margin=margin(0,0,5,0)),
          plot.subtitle = element_text(face="italic", size=12,margin=margin(0,0,9,0)),
          strip.text.x = element_text(face="bold",
                                      size=16, 
                                      color="white",
                                      margin=margin(9,0,9,0))) +
  labs(x = "Covered Recipient Type",
       y = "Number of Payments",
       title = "Number of Payments to Each Type of Covered Recipient",
       subtitle = "By Year") +
  scale_y_continuous(labels=scales::comma)


```



```{r,fig.height=6,fig.width=8}


both  %>% group_by(year) %>%
  mutate(total = sum(n)) %>%
  mutate(prop = n/total) %>%
  mutate(Covered_Recipient_Type= gsub("Covered Recipient ", "",
                                      Covered_Recipient_Type)) %>%
  ggplot(aes(x= factor(year),
             y = prop,
             fill = Covered_Recipient_Type)) +
  geom_bar(stat="identity", position="stack") +
  theme_c(axis.text.x=element_text(size=13),
          axis.title = element_text(size=13),
          plot.title = element_text(face="bold", hjust = .5, size=14, margin=margin(0,0,5,0)),
          plot.subtitle = element_text(face="italic", size=12,margin=margin(0,0,9,0))) +
  labs(y="Proportion of Payments",
       x="Year",
       fill = "Covered Recipient Type",
       title = "Proportion of Payments Going to Each Covered Recipient Type",
       subtitle = "By Year") +
  viridis::scale_fill_viridis(discrete=TRUE,end=.97)


```




## By Primary Type



```{r,fig.width=11,fig.height=6}

########################################
# faceted provider type by year plot
########################################

primary_type_summary_2019$year <- 2019
primary_type_summary_2021$year <- 2021


both_primary <- primary_type_summary_2021 %>%
  bind_rows(primary_type_summary_2019)

both_primary <- both_primary %>%
  mutate(primary = case_when(
    n < 500~  "Other", 
    Covered_Recipient_Primary_Type_1 == "" & 
      Covered_Recipient_Type =="Covered Recipient Teaching Hospital"   ~ "Teaching Hospital",
    TRUE ~ Covered_Recipient_Primary_Type_1))




primary_by_broader_type <- both_primary %>%
  group_by(primary) %>%
  summarize(n_prof = n_distinct(Covered_Recipient_Type),
            prof = paste0(unique(Covered_Recipient_Type), collapse=",")) %>%
  arrange(prof)



library(cowplot)
colors <- as.list(RColorBrewer::brewer.pal("Set3", n=12))

names(colors) <- primary_by_broader_type$primary
colors$`Doctor of Osteopathy` <- "#6074AD"

plt_1 <- both_primary %>%
  filter(Covered_Recipient_Type == "Covered Recipient Non-Physician Practitioner" &
           primary != "Other") %>%
  ggplot(aes(x=Covered_Recipient_Type, y = n, fill = primary)) +
  geom_bar(stat="identity") +
  scale_fill_manual(values=colors, name = 'Non-Physician Practitioner')

l1 <- get_legend(plt_1)


plt_2 <- both_primary %>%
  filter(Covered_Recipient_Type == "Covered Recipient Physician" & primary !="Other") %>%
  ggplot(aes(x=Covered_Recipient_Type, y = n, fill = primary)) +
  geom_bar(stat="identity")+
  scale_fill_manual(values = colors, name ='Physician')


l2 <- get_legend(plt_2)


plt_3 <- both_primary %>%
  filter(primary%in% c("Other", "Teaching Hospital")) %>%
  ggplot(aes(x=Covered_Recipient_Type, y = n, fill = primary)) +
  geom_bar(stat="identity")+
  scale_fill_manual(values = colors, name ='') +
  guides(fill = guide_legend(nrow=6, ncol=2))

l3 <- get_legend(plt_3)


legends <- plot_grid(l1,l2, l3, nrow=3)



plt <- both_primary %>%
  mutate(primary = factor(primary, levels=primary_by_broader_type$primary)) %>%
  mutate(Covered_Recipient_Type= gsub("Covered Recipient ", "",
                                      Covered_Recipient_Type),
         Covered_Recipient_Type = gsub(" ", "\n", Covered_Recipient_Type),
         Covered_Recipient_Type = factor(Covered_Recipient_Type,
                                         levels = c("Physician",
                                                    "Non-Physician\nPractitioner",
                                                    "Teaching\nHospital"))) %>%
  ggplot(aes(x= fct_reorder(Covered_Recipient_Type,n, max,.desc=TRUE),
             fill =primary,
             y = n)) +
  geom_bar(stat="identity",position="stack") +
  facet_grid(~year, space="free", scales="free_y") +
  theme_c(axis.title.x = element_text(margin=margin(15,0,0,0),
                                      size=15),
          axis.text.x=element_text(size=12),
          axis.title.y =element_text(size=15,angle=90),
           plot.title = element_text(face="bold", hjust = .5, size=14, margin=margin(0,0,5,0)),
          plot.subtitle = element_text(face="italic", size=12,margin=margin(0,0,9,0)),
          strip.text.x = element_text(face="bold",
                                      size=16, 
                                      color="white",
                                      margin=margin(9,0,9,0)),
          legend.position="none") +
  scale_fill_manual(values=colors) +
  labs(x = "Covered Recipient Type",
       y = "Number of Payments",
       title = "Number of Payments to Each Type of Covered Recipient",
       subtitle = "By Year") +
  scale_y_continuous(labels=scales::comma) +
  guides(fill = guide_legend(byrow=FALSE, nrow =5))


plot_grid(plt, legends,  ncol=2, rel_widths=c(.8,.2))


```


```{r,eval=FALSE}


###############################################################
# ITERATE BY CHUNK TO HANDLE LARGE FILE SIZES (2019)
###############################################################

# get number of rows in full dataset in the terminal with:
# wc -l OP_DTL_GNRL_PGYR2021_P01202023.csv
chunk_size <- ceiling(1140813/20)

chunks <- tibble(end = (1:20)*chunk_size) %>%
  mutate(begin =  lag(end,n=1)) %>%
  # first observation will have NA observation when we lag
  # so set this one to 1
  mutate(begin = ifelse(is.na(begin),1, begin),
         begin =ifelse(begin!=1, begin+1, begin))



type_summary <- pmap_df(chunks, function(begin,end) {
  
  message(paste("skip =", begin, "end_index = ",begin+chunk_size))
  
    dat <- data.table::fread(here('data/OP_DTL_GNRL_PGYR2021_P01202023.csv'),
          skip = begin,
          nrows = chunk_size,
          col.names = general_names,
          colClasses="character") 
    # number of payments in each category
    by_type <- dat %>%
      group_by(Covered_Recipient_Type) %>%
      summarize(n = n())
  })




type_summary_2021 <- type_summary %>%
  group_by(Covered_Recipient_Type) %>%
  summarize(n = sum(n)) 



```




```{r,eval=FALSE}

# to try to get by id we would need to go over entire dataset
type_summary <- pmap_df(chunks, function(begin,end) {
  
  message(paste("skip =", begin, "end_index = ",begin+chunk_size))
  
    dat <- data.table::fread(here('data/OP_DTL_GNRL_PGYR2021_P01202023.csv'),
          skip = begin,
          nrows = chunk_size,
          col.names = general_names,
          colClasses="character") %>%
      mutate(ID = case_when(
        Covered_Recipient_Type ==  "Covered Recipient Teaching Hospital" ~Teaching_Hospital_ID,
        # NPI almost always reported, but this catches cases where it is blank
        Covered_Recipient_NPI != "" ~ Covered_Recipient_NPI,
        Covered_Recipient_NPI == "" ~ Covered_Recipient_Profile_ID))
    by_type <- dat %>%
      group_by(Covered_Recipient_Type) %>%
      summarize(number_ids_in_type = n_distinct(ID))
  })

```


```{r,eval=FALSE}


distinct_rows <- test %>% distinct() %>% nrow()
all_rows <-  test %>%  nrow()

distinct_rows==all_rows


# no observations are blank in all 3
dat %>% filter(Covered_Recipient_Profile_ID == "" &Teaching_Hospital_ID=="" & Covered_Recipient_NPI=="") %>% as_tibble() %>% glimpse()




general %>%
  filter(grepl("Johnson", Applicable_Manufacturer_or_Applicable_GPO_Making_Payment_Name)) %>%
  mutate(date = as_date(Date_of_Payment, format = "%m/%d/%Y")) %>%
  filter(Nature_of_Payment_or_Transfer_of_Value == "Food and Beverage") %>%
  group_by(date) %>%
  mutate(n=n()) %>%
  ungroup() %>%
  filter(n==max(n)) %>% 
  select(Total_Amount_of_Payment_USDollars, date,Covered_Recipient_NPI,n) %>%
  filter(date=="2021-10-04")
  


general %>%
  filter(
    Applicable_Manufacturer_or_Applicable_GPO_Making_Payment_Name ==
           max_example$Applicable_Manufacturer_or_Applicable_GPO_Making_Payment_Name & 
           date ==max_example$date & 
           Nature_of_Payment_or_Transfer_of_Value == "Food and Beverage") %>%
  as_tibble() %>%
  select(Total_Amount_of_Payment_USDollars,Covered_Recipient_NPI,date, 
         company = Applicable_Manufacturer_or_Applicable_GPO_Making_Payment_Name) %>%
  group_by(Total_Amount_of_Payment_USDollars,company) %>%
  summarize(n=n()) %>%
  arrange(desc(n))
# 
# for
# 11,408,131
# 
# 1:1e3
# 
# 1e3

v <- rep(1:1e3, 1000000)


general %>%
  select(Submitting_Applicable_Manufacturer_or_Applicable_GPO_Name ) %>%
  distinct() %>%
  group_by(Submitting_Applicable_Manufacturer_or_Applicable_GPO_Name) %>%
  summarize(n=n()) %>%
  arrange(desc(n))


  filter(grepl("Amgen", Submitting_Applicable_Manufacturer_or_Applicable_GPO_Name))

```

```{r,eval=FALSE}
library(sqldf)

filter = 'tr.exe -d \'^"\' '

iris2 <- read.csv.sql('data/OP_DTL_GNRL_PGYR2021_P01202023.csv', 
    sql = "select * from file where Submitting_Applicable_Manufacturer_or_Applicable_GPO_Name = 'Genetech, Inc.' ",
    nrows=50)


df <- data.table::fread('data/OP_DTL_GNRL_PGYR2021_P01202023.csv', nrows)

```

